Data exploration through dot-driven development\footnote{This work was supported by Google Digital News Initiative.}

### 2017-01-13 pivot/paper.tex
One more typo

The core language uses type providers, but we employ them in a novel way -- rather than providing 
types with members for accessing data, we provide types with members that allow the user to also 
compose rich and correct queries using just member access (``dot''). This way, we recreate 
functionality that usually requires complex type systems (row polymporphism, type state and dependent 
typing) in an extremely simple object-based language.

>>>>

The core language uses type providers, but we employ them in a novel way -- rather than providing 
types with members for accessing data, we provide types with members that allow the user to also 
compose rich and correct queries using just member access (``dot''). This way, we recreate 
functionality that usually requires complex type systems (row polymorphism, type state and dependent 
typing) in an extremely simple object-based language.
